Fig1

### 2020-05-12 analysis/figure-1.Rmd
small tests working. like these new plots
removing old themes and functions

source("../R/themes.R")
source("../R/functions.R")
#source("../R/wrangledata.R")

@@

@@

theme_B3 <- function () { 
  theme_classic(base_size = 20,
                base_family = 'Helvetica') +
    theme(
      strip.background  = element_blank(),
      panel.grid.major  = element_blank(),  # remove major gridlines
      panel.grid.minor  = element_blank()  # remove minor gridlines
    )
}
# hyp
d2 <- makebargraph("hypothalamus","DEGs w/ + LFC", 0, 4300) + 
  theme(axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank())  +
  labs(subtitle = " ")
# pit
d4 <- makebargraph("pituitary","DEGs w/ + LFC", 0, 4300)  +  
  theme(axis.ticks = element_blank(),
        axis.text.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())  +
  labs(subtitle = " ")
# gon
d6 <- makebargraph("gonad","DEGs w/ + LFC", 0, 4300) +  
  theme(axis.ticks = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlabels)+
  labs(subtitle = " ")

d6

>>>>

source("../R/themes.R")
source("../R/functions.R")

@@

## import limma counts and sample info

```{r data}
countData <- read_csv("../results/01_limma.csv") %>%
  column_to_rownames(var = "X1")
countData <- as.data.frame(t(countData))
head(countData[1:3])

colData <- read_csv("../metadata/00_colData.csv") %>%
  mutate(treatment = factor(treatment, levels = alllevels),
         tissue = factor(tissue, levels = tissuelevels)) %>% 
  column_to_rownames(var = "X1") 
head(colData)
# check ready for analysis
# row.names(countData) == row.names(colData)
head(row.names(countData) == row.names(colData))
```

@@

# hyp
d2 <- makebargraph("hypothalamus","DEGs w/ + LFC", 0, 4300) + 
  theme(axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank())  +
  labs(subtitle = " ")
# pit
d4 <- makebargraph("pituitary","DEGs w/ + LFC", 0, 4300)  +  
  theme(axis.ticks = element_blank(),
        axis.text.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())  +
  labs(subtitle = " ")
# gon
d6 <- makebargraph("gonad","DEGs w/ + LFC", 0, 4300) +  
  theme(axis.ticks = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlabelschar)+
  labs(subtitle = " ")
